Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-17 paper/ms.tex
ms: add appendix

Once a star's period was identified, we binned the phased light curve
to 100 points per cycle.  To separate ``sharp'' local minima from
smooth but double-dipped spot variability, we then iteratively fit
robust penalized splines to the wrapped phase-folded light curve,
excluding points more than two standard deviations away from the local
continuum \citep{2019AJ....158..143H}.  The maximum number of
equidistant spline knots per cycle is the parameter in this framework
that controlled the meaning of ``sharp'' --- we allowed at most 10
such knots per cycle, though for most stars fewer knots were preferred
based on cross-validation using an $\ell^2$-norm penalty.  An example
fit is shown in panel {\it (e)} of Figure~\ref{fig:vet}.

@@

To identify local minima near the edges of the phased light curve,
which usually would cover phases $\phi \in [ 0,1 ]$, we performed the
entire procedure over a phase-folded light curve spanning $\phi \in
[-1,2 ]$, by duplicating and concatenating the ordinary phase-folded
light curve.  The free parameters we adopted throughout this analysis
procedure, for instance the maximum number of spline knots per cycle,
and how large and wide of a local minimum to consider a ``true dip'',
were chosen during testing based on their ability to correctly
re-identify a large fraction ($>$90\%) of known CQVs, while also being
able to consistently reject common false positives such as rapidly
rotating spot-induced variability and typical eclipsing binaries.

@@

We performed an independent search for strongly periodic phenomena
using a Fourier-based approach, following \citet{2019ApJ...876..127Z}
and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
the {\tt PDC\_SAP} light curves, we normalized each light curve, and
then re-binned it into equal width 120-second bins to account for the
uneven spacing in the TESS data, as well as the data gap caused by
satellite downlink during each sector.  We then padded the data to
ensure that the light curve had a length that was a power of two, as
described by \citeauthor{2019ApJ...876..127Z}.  Taking the Fourier
transform of the corrected, padded light curve using {\tt
numpy.fft.fft}, we then searched for peaks with a significance of over
12-$\sigma$ within a set of 500 frequency bins.

If a peak of such significance was found, we generated a ``summary
sheet'' with information about the star, its full and folded light
curves, Fourier transform, potential contaminating stars, and
information about these contaminating stars.  In the sectors for which
we performed this analysis, we found that ``summary'' sheets were
generated for $\approx$10\% of the 20\,000 120-second targets in a
given sector.  We then manually reviewed each summary sheet, and
visually labelled each star based on its morphology (including e.g.,
eclipsing binary, CQV, RS CVn, or cataclysmic variable).  CQVs that
were observed in multiple sectors had their light curves stitched
together and analyzed for a more accurate period determination.

@@

Broadly speaking, the most common false positives for both the Fourier
and dip-counting techniques were eclipsing binaries, spot-induced
variability from rapid rotators, and variability from neighboring,
off-target stars.  Typical false positive rates from our dip-counting
pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and
about 20\% being labeled either ``good'' or ``possible'' CQVs.  The
Fourier analysis was not amenable to calculating a similar
false-positive rate, because it was implemented as a general
variability search; its results are also being used for analyses on
topics other than CQVs.

@@

\paragraph{Ages}
We estimated the stellar ages by making probabilistic spatial and
kinematic associations between the CQVs and known clusters in the
solar neighborhood.  For most stars in our sample, we did this using
BANYAN\,$\Sigma$
\citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
git commit \texttt{394b486}} This algorithm calculates the probability
that a given star belongs to one of 27 young clusters (or
``assocations'') within 150\,pc of the Sun, by modeling the clusters
as multivariate Gaussians in 3-D position and 3-D velocity space.  We
used the Gaia DR2 sky positions, proper motions, and distances to
calculate the membership probabilities.  BANYAN\,$\Sigma$ in turn
analytically marginalizes over the radial velocity dimension.  The
probabilities returned by this procedure are qualitatively useful, but
should be assessed with caution due to the non-Gaussian nature of most
groups within the solar neighborhood \citep[see
e.g.][Figure~10]{2021ApJ...917...23K}.

@@

With the effective temperatures and stellar radii from the SED fit, we
then estimated the stellar masses by interpolating against the PARSEC
isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
that incorporate some form of correction for young, active M dwarfs is
well-documented
\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
Plausible explanations for anomalous M dwarf colors and sizes relative
to model predictions include starspot coverage
\citep[e.g.][]{2017ApJ...836..200G}, and potentially incomplete line
lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
\citet{2014MNRAS.444.2525C} performed an empirical correction to the
temperature--opacity relation drawn from the BT-Settl model
atmospheres, in order to match observed masses and radii of younq
eclipsing binaries.  This is sufficient for our goal of estimating
stellar masses.  Given our observed $\{ \tilde{T}_{\rm eff},
\tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$
and $\sigma_{\tilde{t}}$, we evaluate a distance $d$ between our
observations and any model PARSEC grid-point $\{ T_{\rm eff}, M_\star,
t \}$ as
\begin{equation}
  d^2 = 
  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
  +
  \left( \frac{\tilde{M}_{\star} - M_{\star}}{\sigma_{\tilde{M}_{\star}}} \right)^2
  +
  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
\end{equation}
in order to assign equal importance to each dimension.  The preferred
model mass is then one that minimizes this distance, and is quoted in
Table~\ref{tab:thetable}.  Uncertainties in the masses are propagated
forward from the statistical uncertainties in the radii, temperatures,
and ages.

@@

{\it Multiple periodic TESS signals}---During our visual analysis of
the TESS light curves and PDM periodograms, we flagged sources with
beating light curves, and with PDM periodograms that showed multiple
periods.  We also attempted to disentangle the two signals by
subtracting the mean CQV signal over each sector, and then repeating
the phase-dispersion minization analysis.  The results of this effort
are summarized in the secondary periods, $P_{\rm sec}$, listed in
Table~\ref{tab:thetable}.  This process yielded
\ngoodmultperiodflag/\ngoods\ high-quality CQVs with secondary
periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous sample met
the same criterion.  Of the \ngoodhighruwe\ good CQVs with RUWE$_{\rm
DR3}$ $>$ 2, \ngoodruweandmultperiod\ also showed secondary periods in
the TESS light curves.  Considering the weaker threshold of RUWE$_{\rm
DR3}$ $>$ 1.4, \ngoodweakruweandmultperiod/\ngoodweakruwe\ such CQVs
showed secondary TESS periods.

@@

There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
two highly structured dip complexes, plus a small leading dip.  The
single leading dip is present at the same phase as in cycles 0-64, and
is therefore likely to be the same struture.  Along a similar line of
logic, it seems plausible that the first ``dip complex'' during cycles
248-264 represents an evolution of the initial complex seen during
cycles 0-64, though with reduced depth.  During cycles 266-310, an
additional local minimum develops between the two complexes; this
feature is best visualized on the river plots
(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period
below.

@@

Independent of the microphysical basis for gas absorption, the
observed lifetime of the CQV phenomenon could provide another
dimension to discern between the gas {\it vs.} dust clump scenarios.
Based on the available statistics from e.g.
\citet{2022AJ....164...80R} and references therein, it seems plausible
that CQV occurrence decreases in time, bottoming to zero well before
the $\approx$700\,Myr age of Praesepe.  This is odd in the context of
the prominence scenario, because pre-main-sequence M dwarfs spin up
over the first $\approx$$10^8$\,yr; prominences might even be expected
to be {\it more} common at the age of the Pleiades than for younger
stars.  This broadly assumes that any star that can support
prominences will do so, and that the magnetic topology of rapidly
rotating M dwarfs at 100\,Myr is similar to that of rapidly rotating M
dwarfs at say, 10\,Myr.  Based on the degree to which M dwarfs remain
rapid rotators over the first few gigayears of their lives
\citep[e.g.][]{2022AJ....164...80R,2022ApJ...936..109P}, it seems
surprising in the gas clump (prominence) scenario that very few stars
older than 150\,Myr have been seen to exhibit the phenomenon.  In the
dust clump scenario this is not a problem, because if the dust were
externally sourced, it would be expected to have a finite supply.

@@

Given this context, it is tempting to try to interpret features of the
CQV light curves in terms of the possible presence of either close-in
exoplanets or close-in planetesimals.  Rocky planets this young could
have molten global magma oceans analogous to those that existed on the
Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus might be
undergoing significant outgassing and atmospheric escape.  The system
would then be analogous to the Jupiter-Io plasma torus
\citep[e.g.][]{1980JGR....85.1171N}, although with magnetic fields
stronger by a factor of $\approx$1{,}000.  However we emphasize that
while this type of configuration seems {\it a priori} plausible, no
direct evidence currently supports it.

@@

		\vspace{-0.1cm}
		\caption{
      {\bf The magnetic B star connection.}
      $\sigma$~Ori~E and HD~345439 (top row) are magnetic B stars with
      predominantly dipolar magnetic fields known to host
      circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
      are analogous magnetic B stars with field toplogies dominated by
      high order multipoles.  The bottom row compares the latter
      systems against the ``best-matching'' CQV light curves, selected
      by eye from Figure~\ref{fig:cqvs}.  CQVs have light curves that
      are visually similar to the topologically complex magnetic B
      stars.  Stellar masses rounded to one significant figure are
      given in the lower right of each panel; the star, TESS sector,
      and period are listed in each subtitle.
		}
		\label{fig:bstar}
	\end{center}
\end{figure}

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Bona fide, candidate, and debunked complex quasiperiodic
  variables from the TESS 2-minute data. {\bf For internal
  review, full versions are available here
  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}} \label{tab:thetable}}
%\toprule
%TIC & $T$ & $d$ & BP-RP & RUWE & $P$ & assoc & age & teff & rstar & mstar & rcr & qual & Nsectors \\
%\midrule
%\endhead
\startdata
  TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & $P_{\rm sec}$ & Quality & Bin & $N_{\rm sector}$ \\
  -- &   mag & pc &    mag &      -- &        hr &   -- &        Myr &  K                  & $R_\odot$ & $M_\odot$ & $R_\star$         & hr                     & -- & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality}
  flag 1), \nmaybes\ ambiguous CQVs (\texttt{Quality} flag 0), and
  \ndebunked\ impostors (\texttt{Quality} flag -1).  The three-bit
  binarity flag ``Bin'' is for Gaia DR3
  \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
  \texttt{ruwe} outliers (bit 2), and stars with multiple TESS periods
  (bit 3).  The machine-readable version, available online, includes
  additional columns for the Gaia DR2 and DR3 source identifiers, as
  well as the stellar parameter uncertainties.  The age uncertainties
  are typically $\approx \pm 10\%$, but can be asymmetric.  The median
  statistical uncertainties on the temperature, radius, and mass are
  $\pm$50\,K, $\pm$4\% and $\pm$9\% respectively.
  $N_{\rm sector}$ denotes the number of TESS sectors for which {\it
  any} data are expected to be acquired between July~2018 and
  Oct~2024.  This number is generally greater than the number of
  sectors for which 120-second cadence data exist.   Association names
  and provenance follow conventions adopted by
  \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	%APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
  CARN: Carina Near moving group \citep{2006ApJ...649L.115Z}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
	The ``(?)'' string denotes low-confidence membership.
}
\end{deluxetable}
\clearpage

@@

%\section{Validation plots}
%\label{app:vetting}
%
%Figure~\ref{fig:vet} shows the type of plot used to visually assess
%whether a source was likely to be a CQV, eclipsing binary, or simply a
%rapidly rotating star.
%
%\begin{figure*}[!t]
%	\begin{center}
%    \centering
%    \includegraphics[width=0.96\textwidth]{annotated_402980664_S0018_120sec_cpvvetter.pdf}
%		\vspace{-0.45cm}
%		\caption{
%      {\bf Validation plots used to manually label CQVs}.  The complete figure
%      set, with one image per sector for each of \ncpvsfound\ CQVs
%      and candidate CQVs
%      is available online {\bf For internal collaboration review:
%      \url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
%      Panels are as follows.
%      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
%      data and black points are binned to 200 points per cycle.
%      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
%      Dotted lines show up to the 10$^{\rm th}$ harmonic and
%      subharmonic.
%      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
%      circles displayed for scale.
%      {\it d)}: Cleaned light curve, binned to 20-minute cadence, in
%      Barycentric TESS Julian Date (BTJD).
%      {\it e)}: Phase-folded light curve, binned to 100 points per
%      cycle.  The gray line denotes the automated spline-fit to the
%      wrapped phase-folded light curve, and small gray triangles
%      denote automatically identified local minima.
%      {\it f)}: Phase-folded light curve at twice the peak period.
%      {\it g)}: Phase-folded light curve at half the peak period.
%      {\it h)}: Phase-folded time-series within the ``background''
%      aperture defined in the SPOC light curves.
%      {\it i)}: Phase-folded flux-weighted centroid in the column
%      direction.
%      {\it j)}: Phase-folded flux-weighted centroid in the row
%      direction.
%      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
%      The gray background denotes stars within 100\,pc.
%      {\it l)}: Information from Gaia DR2, TIC8, and the automated
%      dip-counting search pipeline.  ``Neighbors'', abbreviated
%      ``nbhr'', are listed within apparent distances of 2 TESS pixels
%      if $\Delta T$$<$2.5.
%      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
%      using positions, proper motions, and the parallax.
%      }
%		\label{fig:vet}
%	\end{center}
%\end{figure*}

@@

>>>>

Once a star's period was identified, we binned the phased light curve
to 100 points per cycle.  To separate ``sharp'' local minima from
smooth spot-induced variability, we then iteratively fit
robust penalized splines to the wrapped phase-folded light curve,
excluding points more than two standard deviations away from the local
continuum \citep{2019AJ....158..143H}.  The maximum number of
equidistant spline knots per cycle is the parameter in this framework
that controlled the meaning of ``sharp'' --- we allowed at most 10
such knots per cycle, though for most stars fewer knots were preferred
based on cross-validation using an $\ell^2$-norm penalty.  An example
fit is shown in panel {\it (e)} of Figure~\ref{fig:vet}.

@@

To identify local minima near the edges of the phased light curve,
which usually would cover phases $\phi \in [ 0,1 ]$, we performed the
entire procedure over a phase-folded light curve spanning $\phi \in
[-1,2 ]$, by duplicating and concatenating the ordinary phase-folded
light curve.  The free parameters we adopted throughout this analysis
procedure, for instance the maximum number of spline knots per cycle,
and how large and wide of a local minimum to consider a ``true dip'',
were chosen during testing based on their ability to correctly
re-identify a large fraction ($>$90\%) of previously known CQVs, while also being
able to consistently reject common false positives such as rapidly
rotating spot-induced variability and typical eclipsing binaries.

@@

We performed an independent search for strongly periodic phenomena
using a Fourier-based approach, following \citet{2019ApJ...876..127Z}
and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
the {\tt PDC\_SAP} light curves, we normalized each light curve, and
then re-binned it into equal width 120-second bins to account for the
uneven spacing in the TESS data, as well as the data gap caused by
satellite downlink during each sector.  We then padded the data to
ensure that the light curve had a length that was a power of two, as
described by \citeauthor{2019ApJ...876..127Z}.  Taking the Fourier
transform of the corrected, padded light curve using {\tt numpy.fft},
we then searched for peaks with a significance of over 12-$\sigma$
within a set of 500 frequency bins.

If a peak of such significance was found, we generated a ``summary
sheet'' with information about the star, its full and folded light
curves, Fourier transform, potential contaminating stars, and
information about these contaminating stars.  In the sectors for which
we performed this analysis, we found that ``summary'' sheets were
generated for $\approx$10\% of the 20{,}000 120-second targets in a
given sector.  We then manually reviewed each summary sheet, and
visually labeled each star based on its morphology (including e.g.
eclipsing binary, CQV, RS CVn, or cataclysmic variable).  CQVs that
were observed in multiple sectors had their light curves stitched
together and analyzed for a more accurate period determination.

@@

Broadly speaking, the most common false positive triggers for both the Fourier
and dip-counting techniques were eclipsing binaries, spot-induced
variability from rapid rotators, and variability from neighboring,
off-target stars.  Typical false positive rates from our dip-counting
pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and
about 20\% being labeled either ``good'' or ``possible'' CQVs.  The
Fourier analysis was not amenable to calculating a similar
false-positive rate, because it was implemented as a general
variability search; its results are also being used for analyses on
topics other than CQVs.

@@

\paragraph{Ages}
We estimated the stellar ages by making probabilistic spatial and
kinematic associations between the CQVs and known clusters in the
solar neighborhood.  For most stars in our sample, we did this using
BANYAN\,$\Sigma$
\citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
git commit \texttt{394b486}} This algorithm calculates the probability
that a given star belongs to one of 27 young clusters (or
``associations'') within 150\,pc of the Sun, by modeling the clusters
as multivariate Gaussians in 3-D position and 3-D velocity space.  We
used the Gaia DR2 sky positions, proper motions, and distances to
calculate the membership probabilities.  BANYAN\,$\Sigma$ in turn
analytically marginalizes over the radial velocity dimension.  The
probabilities returned by this procedure are qualitatively useful, but
should be assessed with caution due to the non-Gaussian nature of most
groups within the solar neighborhood \citep[see
e.g.][Figure~10]{2021ApJ...917...23K}.

@@

With the effective temperatures and stellar radii from the SED fit, we
then estimated the stellar masses by interpolating against the PARSEC
isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
that incorporate some form of correction for young, active M dwarfs is
well-documented
\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
Plausible explanations for anomalous M dwarf colors and sizes relative
to model predictions include starspot coverage
\citep[e.g.][]{2017ApJ...836..200G}, and potentially incomplete line
lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
\citet{2014MNRAS.444.2525C} performed an empirical correction to the
temperature--opacity relation drawn from the BT-Settl model
atmospheres, in order to match observed masses and radii of young
eclipsing binaries.  This is sufficient for our goal of estimating
stellar masses.  Given our observed $\{ \tilde{T}_{\rm eff},
\tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$
and $\sigma_{\tilde{t}}$, we evaluate a distance $d$ between our
observations and any model PARSEC grid-point $\{ T_{\rm eff}, M_\star,
t \}$ as
\begin{equation}
  d^2 = 
  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
  +
  \left( \frac{\tilde{M}_{\star} - M_{\star}}{\sigma_{\tilde{M}_{\star}}} \right)^2
  +
  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
\end{equation}
in order to assign equal importance to each dimension.  The preferred
model mass is then one that minimizes this distance, and is quoted in
Table~\ref{tab:thetable}.  Uncertainties in the masses are propagated
forward from the statistical uncertainties in the radii, temperatures,
and ages.

@@

{\it Multiple periodic TESS signals}---During our visual analysis of
the TESS light curves and PDM periodograms, we flagged sources with
beating light curves, and with PDM periodograms that showed multiple
periods.  We also attempted to disentangle the two signals by
subtracting the mean CQV signal over each sector, and then repeating
the phase-dispersion minimization analysis.  The results of this effort
are summarized in the secondary periods, $P_{\rm sec}$, listed in
Table~\ref{tab:thetable}.  This process yielded
\ngoodmultperiodflag/\ngoods\ high-quality CQVs with secondary
periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous sample met
the same criterion.  Of the \ngoodhighruwe\ good CQVs with RUWE$_{\rm
DR3}$ $>$ 2, \ngoodruweandmultperiod\ also showed secondary periods in
the TESS light curves.  Considering the weaker threshold of RUWE$_{\rm
DR3}$ $>$ 1.4, \ngoodweakruweandmultperiod/\ngoodweakruwe\ such CQVs
showed secondary TESS periods.

@@

There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
two highly structured dip complexes, plus a small leading dip.  The
single leading dip is present at the same phase as in cycles 0-64, and
is therefore likely to be the same structure.  Along a similar line of
logic, it seems plausible that the first ``dip complex'' during cycles
248-264 represents an evolution of the initial complex seen during
cycles 0-64, though with reduced depth.  During cycles 266-310, an
additional local minimum develops between the two complexes; this
feature is best visualized on the river plots
(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period
below.

@@

Independent of the microphysical basis for gas absorption, the
observed lifetime of the CQV phenomenon could provide another
dimension to discern between the gas vs.~dust clump scenarios.
Based on the available statistics from e.g.
\citet{2022AJ....164...80R} and references therein, it seems plausible
that CQV occurrence decreases in time, bottoming to zero well before
the $\approx$700\,Myr age of Praesepe.  This is odd in the context of
the prominence scenario, because pre-main-sequence M dwarfs spin up
over the first $\approx$$10^8$\,yr; prominences might even be expected
to be {\it more} common at the age of the Pleiades than for younger
stars.  This broadly assumes that any star that can support
prominences will do so, and that the magnetic topology of rapidly
rotating M dwarfs at 100\,Myr is similar to that of rapidly rotating M
dwarfs at say, 10\,Myr.  Based on the degree to which M dwarfs remain
rapid rotators over the first few gigayears of their lives
\citep[e.g.][]{2022AJ....164...80R,2022ApJ...936..109P}, it seems
surprising in the gas clump (prominence) scenario that very few stars
older than 150\,Myr have been seen to exhibit the phenomenon.  In the
dust clump scenario this is not a problem, because if the dust were
externally sourced, it would be expected to have a finite supply.

@@

Given this context, it is tempting to try to interpret features of the
CQV light curves in terms of the possible presence of either close-in
exoplanets or close-in planetesimals.  Rocky planets this young could
have molten global magma oceans analogous to those that existed on the
Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus might be
undergoing significant outgassing and atmospheric escape.  The system
would then be analogous to the Jupiter-Io plasma torus
\citep[e.g.][]{1980JGR....85.1171N}, although with magnetic fields
stronger by a factor of $\approx$1{,}000.  However we emphasize that
while this type of configuration seems a priori plausible, no
direct evidence currently supports it.

@@

		\vspace{-0.1cm}
		\caption{
      {\bf The magnetic B star connection.}
      $\sigma$~Ori~E and HD~345439 (top row) are magnetic B stars with
      predominantly dipolar magnetic fields known to host
      circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
      are analogous magnetic B stars with field topologies dominated by
      high order multipoles.  The bottom row compares the latter
      systems against the ``best-matching'' CQV light curves, selected
      by eye from Figure~\ref{fig:cqvs}.  CQVs have light curves that
      are visually similar to the topologically complex magnetic B
      stars.  Stellar masses rounded to one significant figure are
      given in the lower right of each panel; the star, TESS sector,
      and period are listed in each subtitle.
		}
		\label{fig:bstar}
	\end{center}
\end{figure}

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Bona fide, candidate, and debunked complex quasiperiodic
  variables from the TESS 2-minute data. {\bf For internal
  review, full versions are available here
  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}} \label{tab:thetable}}
%\toprule
%\midrule
%\endhead
\startdata
  TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & $P_{\rm sec}$ & Quality & Bin & $N_{\rm sector}$ \\
  -- &   mag & pc &    mag &      -- &        hr &   -- &        Myr &  K                  & $R_\odot$ & $M_\odot$ & $R_\star$         & hr                     & -- & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality}
  flag 1), \nmaybes\ ambiguous CQVs (\texttt{Quality} flag 0), and
  \ndebunked\ impostors (\texttt{Quality} flag -1).  The three-bit
  binarity flag ``Bin'' is for Gaia DR3
  \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
  \texttt{ruwe} outliers (bit 2), and stars with multiple TESS periods
  (bit 3).  The machine-readable version, available online, includes
  additional columns for the Gaia DR2 and DR3 source identifiers, as
  well as the stellar parameter uncertainties.  The age uncertainties
  are typically $\approx \pm 10\%$, but can be asymmetric.  The median
  statistical uncertainties on the temperature, radius, and mass are
  $\pm$50\,K, $\pm$4\% and $\pm$9\% respectively.
  $N_{\rm sector}$ denotes the number of TESS sectors for which {\it
  any} data are expected to be acquired between July~2018 and
  Oct~2024.  This number is generally greater than the number of
  sectors for which 120-second cadence data exist.   Association names
  and provenance follow conventions adopted by
  \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	%APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
  CARN: Carina Near moving group \citep{2006ApJ...649L.115Z}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
	The ``(?)'' string denotes low-confidence membership.
}
\end{deluxetable}

@@

@@

\section{The CQVs are not obviously accreting}

We acquired iodine-free reconnaissance spectra using Keck/HIRES for
three CQVs.  The goals were to determine the chromospheric activity
levels, and to check for indications of either accretion or
spectroscopic binarity.  We acquired a 15 minute exposure of
TIC~146539195 on 2023 January 3, a 15 minute exposure of TIC~264599508
on 2023 January 9, and a 30 minute exposure of TIC~402980664 on 2023
July 10.  The acquisition and analysis followed the usual techniques
of the California Planet Survey \citep{2010ApJ...721.1467H}.
Figure~\ref{fig:speccutouts} shows cutouts from the resulting spectra,
centered on the \ion{Ca}{2} HK windows, H$\alpha$, and the \ion{Li}{1}
6708\,\AA\ doublet.  The \ion{Ca}{2} H emission line is blended with
H$\epsilon$.  While a more detailed analysis will be left for future
work, these spectra confirm previous understanding established by
\citet{2017AJ....153..152S} that the stars are chromospherically
active M dwarfs in the ``weak-lined'' T Tauri regime
\citep[e.g.][Figure~15]{2019AJ....157...85B}.  Their H$\alpha$
equivalent widths, at $\approx$14\,\AA, $\approx$8\,\AA, and
$\approx$3\AA, are consistent with purely chromospheric emission.
The blue excess in TIC~264599508 could be explained by a second
unresolved star; the TESS light curve for this source shows both the
7.90\,hr CQV signal, and a 9.00\,hr rotation signal with comparable
amplitude.

\begin{figure*}[!t]
	\begin{center}
	\subfloat{
			\includegraphics[width=0.9\textwidth]{f13a.pdf}
    }

	\vspace{-1.1cm}
	\subfloat{
			\includegraphics[width=0.9\textwidth]{f13b.pdf}
    }

	\vspace{-1.1cm}
	\subfloat{
			\includegraphics[width=0.9\textwidth]{f13c.pdf}
    }
	\end{center}
	\vspace{-0.4cm}
	\caption{
		{\bf Activity and age diagnostics for three CQVs}.
		Wavelengths are in air;
		the continuum normalization is relative to the entire order.
		The H$\alpha$ emission strength classifies the stars as weak-lined
		T Tauris.
		The lithium detection for TIC~146539195 is consistent with its
		mass and $\beta$~Pic membership;
		the non-detections for TIC~402980664 and TIC~264599508
		are consistent with the $\sim$42\,Myr age implied by their membership
		in the Columba moving group.
	}
	\label{fig:tic3006timegroups}
\end{figure*}
